\documentclass[10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% KNOWN ISSUES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% * When tools are shown for previous jobs, table alignment is stuffed up.
%------------------------------------------------------------------------------%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INCLUDES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\RequirePackage[l2tabu,orthodox]{nag}

\usepackage[showgrades]{cvtools} % my CV styling stuff
\usepackage[margin=3cm]{geometry}	% extend page margins
\usepackage{graphicx} 				% for graphics
\usepackage[hidelinks]{hyperref} 	% for hyperlinks
\usepackage{verbatim} 				% for block commenting
%------------------------------------------------------------------------------%

% My details
\input{MyDetails}

% Graphics directory
\graphicspath{{./img/}}

% Title details
\title{\Huge{\textbf{\myName}}}
\author{\Large{\underline{Curriculum Vitae}}}
\date{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Objective
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Objective}
To work in a competitive environment that effectively utilizes my analytical, 
interpersonal, leadership and organizational skills to conceive and achieve 
solutions. The solutions which help the organization in not only meeting its 
targets, but also allowing it to grow, thereby, enhancing my own skills as an 
individual and as a key player in the organization's development.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Personal details
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Personal details}
\begin{personalDetails}
\personalDetailsItem{Name}{\myName}
\personalDetailsItem{Date of Birth}{\myDOB}
\personalDetailsItemWithSpace{Address}{\myAddress{\newline}}

\personalDetailsItemWithSpace{Mobile}{\myMobile}

\personalDetailsItem{Email}{\myEmail}
\personalDetailsItem{LinkedIn}{\myLinkedIn}
\personalDetailsItem{GitHub}{\myGithub}
\end{personalDetails}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Summary
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Summary}
\begin{itemize}
\begin{comment}
	\item Currently working as a \jobTitle{Graduate Software Engineer} at the 
		\company{Reserve Bank of Australia}.
\end{comment}
	\item Currently working as a \jobTitle{Tutor} at \company{The University of
		Sydney}.
	\item Currently working as a \jobTitle{Engineering/Data Analytics Intern} at  
		\company{Freelancer.com}.
	\item Will graduate from \educationInstitute{The University of Sydney} with 
		a \qualificationName{Bachelor of Engineering (Computer)} in 2012.
	\item Will graduate from \educationInstitute{The University of Sydney} with 
		a \qualificationName{Bachelor of Science (Computer Science)} in 2012.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Interests
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Interests}
\begin{itemize}
	\item Embedded systems
	\item Computer and network security
	\item Real-time systems
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Technical Skills
%
% \technicalSkillsItem}{itemName}{itemValues}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Technical Skills}
\begin{technicalSkills}

\technicalSkillsItem{Programming Languages}
{
    \item C
    \item C++
    \item Java
    \item \LaTeX
    \item MATLAB
    \item Perl
    \item sed
    \item PHP
    \item Python
    \item JavaScript
    \item x86 Assembly Language
    \item VBA
}

\technicalSkillsItem{Shells}
{
    \item Bash
}

\technicalSkillsItem{Embedded Programming}
{
    \item FreeRTOS
    \item LwIP
    \item ThreadX
    \item NetX
}

\technicalSkillsItem{Web-Based Development}
{
    \item HTML
    \item CSS
    \item JavaScript
    \item Apache
    \item NGINX
}

\technicalSkillsItem{Document markup}
{
    \item \LaTeX
    \item WYSIWYG editors (such as ``Microsoft Word'')
}

\technicalSkillsItem{Databases}
{
    \item Oracle
    \item MySQL
    \item postgreSQL
}

\technicalSkillsItem{Operating Systems}
{
    \item Microsoft Windows
    \item Linux
    \item Solaris
}

\technicalSkillsItem{Debugging}
{
    \item GDB
    \item Valgrind
}

\technicalSkillsItem{Tools and Editors}
{
    \item Git
    \item Subversion
    \item Eclipse IDE
    \item Vim
    \item gedit
}

\end{technicalSkills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional experience
%
% \professionalExperienceItem{startEmploymentPeriod}{endEmploymentPeriod}{position}{company}{jobDescription}{\professionalTool{tool} ...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional Experience}
\begin{professionalExperience}

% Tutor (University of Sydney)
\professionalExperienceItem{August 2012}{present}
{Tutor}{University of Sydney}
{I was a tutor for a first year electrical engineering unit of study, named 
``Foundations of Computer Systems'' (ELEC1601). This position involved preparing
and running three-hour laboratory session with up to 40 students in each 
session.}
{}

% Engineering/Data Analytics Intern (Freelancer.com)
\professionalExperienceItem{July 2012}{present}
{Engineering/Data Analytics Intern}{Freelancer.com}
{My job involved assisting in the design and implementation of software for use
by \company{Freelancer.com}. This included working with other staff to establish
technical specifications, developing the software and performing data analysis 
techniques to improve key business metrics.}
{
    % Programming languages
    \professionalTool{PHP}
    
    % Web development
    \professionalTool{CSS}
    \professionalTool{JavaScript}
    \professionalTool{HTML}
    \professionalTool{AJAX}
    \professionalTool{jQuery}
    \professionalTool{Twitter Bootstrap}
    
    % Web administration
    \professionalTool{NGINX}
    
    % Tools and editors
    \professionalTool{Git}
}

% Tutor (University of Sydney)
\professionalExperienceItem{March 2012}{June 2012}
{Tutor}{University of Sydney}
{I was a tutor for a first year electrical engineering unit of study, named 
``Fundamentals of Electrical and Electronic Engineering'' (ELEC1103). This 
position involved preparing and running two-hour tutoring session with up to 40 
students in each session.}
{}

% Software Engineering Intern (Broadcom)
\professionalExperienceItem{November 2011}{February 2012}
{Software Engineering Intern}{Broadcom}
{This position was a great experience and allowed me to further my experience in
embedded computing. I was involved in developing the SDK for Broadcom's WICED 
module (Wireless Internet Connectivity for Embedded Devices).

I completed two primary tasks during my employment. The major task was porting 
``iperf'' (a network throughput management software) to the WICED development 
system. In addition, I added the capability to trace thread execution of a Real 
Time Operating System.}
{
    % Programming languages
    \professionalTool{C}
    \professionalTool{C++}
    \professionalTool{Perl}
    
    % Embedded programming
    \professionalTool{ThreadX}
    \professionalTool{NetX}
    \professionalTool{FreeRTOS}
    \professionalTool{LwIP}
    
    % Debugging
    \professionalTool{GDB}
    
    % Tools and editors
    \professionalTool{Eclipse IDE}
    \professionalTool{Subversion}
}

% System Administrator (Audinate)
\professionalExperienceItem{April 2011}{July 2012}
{System Administrator}{Audinate}
{In this role I administered various servers running on either Ubuntu Server or 
Sun Solaris. I administered various services including LDAP, ZFS (Zettabyte File
System), IMAP/SMTP (Zimbra) and NFS. I also worked extensively with VMware 
Server during this role.

Through this position, I gained a wide range of experience including website
administration, Unix administration and designing and building dedicated Unix
servers.}
{
    % Programming languages
    \professionalTool{PHP}
    
    % Shells
    \professionalTool{bash}
    
    % Web development
    \professionalTool{HTML}
    \professionalTool{CSS}
    \professionalTool{Joomla}
    
    % Web administration
    \professionalTool{Apache}
    
    % Database
    \professionalTool{MySQL}
    
    % Operating systems
    \professionalTool{Ubuntu Server}
    \professionalTool{Sun Solaris}
    
    % Other
    \professionalTool{Zettabyte File System (ZFS)}
    \professionalTool{Zimbra}
}

% Industrial Student (TransGrid)
\professionalExperienceItem{December 2010}{February 2011}
{Industrial Student}{TransGrid}
{In this position, I worked in the ``Projects (Central Region)'' section. I was 
involved with various projects including earth grid safety inspections and 
progress meetings with contractors.

This work experience was a paid work experience offered as a part of my 
\company{Australian Power Institute} bursary.

Whilst at \company{TransGrid}, I developed a database utility using 
Microsoft Access and Visual Basic to assist the projects team with managing and 
tracking project completion. Whilst VBA is not a sophisticated or complicated
programming language, this was an interesting experience in which I was required
to write some sophisticated temporal SQL queries.}
{
    % Programming languages
    \professionalTool{Visual Basic for Applications (VBA)}
    \professionalTool{SQL}
    
    % Databases
    \professionalTool{Microsoft Access}
}

% Industrial Student (Australian Energy Market Operator)
\professionalExperienceItem{December 2009}{February 2010}
{Industrial Student}{Australian Energy Market Operator}
{I was working in the ``Metering \& Settlements'' team. This team had to deal 
with large amounts of data existing in SQL tables which are updated hourly based 
on real-time monitoring data.

This work experience was a paid work experience offered as a part of my 
\company{Australian Power Institute} bursary.

My main role within the team was working on improving the reliability and 
accuracy of the operations of the team by designing software-based tools to 
allow them to monitor and analyse data. I analysed and reconstructed several 
macro-enabled spreadsheets used by the team to perform important calculations. I
was able to improve the accuracy of the data reported by the spreadsheet and 
greatly improve the running speeds of the tools.}
{
    % Programming languages
    \professionalTool{Visual Basic for Applications (VBA)}
    \professionalTool{SQL}
    
    % Databases
    \professionalTool{Oracle}
}

% Industrial Student (Energy Australia)
\professionalExperienceItem{February 2009}{February 2009}
{Industrial Student}{Energy Australia}
{In this role, I was involved with the ``Intelligent Networks'' division, 
working on an electrical sensing and monitoring system. I was involved with 
analysing system diagrams and attending regular meetings with engineers to 
discuss implementation details for a smart metering device that was being 
developed.

This work experience was a paid work experience offered as a part of my 
\company{Australian Power Institute} bursary.}
{}

% Customer Service Officer (The Hills Shire Council)
\professionalExperienceItem{January 2009}{present}
{Customer Service Officer}{The Hills Shire Council}
{This role involved taking phone calls and handling enquiries regarding the 
council's community halls and other related facilities, as well as entering 
these details into a booking system and handling related activities such as 
invoicing.

My role also involved completing room set ups and pack downs, as well as 
supervising events taking place in the council facilities.}
{}

% Chief Pyrotechnician (Howard & Sons Pyrotechnics)
\professionalExperienceItem{July 2008}{present}
{Chief Pyrotechnician}{Howard \& Sons Pyrotechnics}
{I am a licensed pyrotechnician for a world-class pyrotechnics company. As a 
chief pyrotechnician, I am responsible for many aspects of a pyrotechnics 
display, including:
\begin{itemize}
	\item Managing the worksite and firing site.
	\item Managing the loading and unloading of fireworks.
	\item Dealing directly with clients and suppliers on-site.
	\item Responsibility for all rostered crew on-site.
	\item Responsibility for all Workplace Health \& Safety matters on-site.
\end{itemize}

In addition to my role as a pyrotechnician, I am also a pyrotechnic display 
designer and am responsible for the planning, designing and choreography of a 
pyrotechnics display to musical soundtracks.}
{}

% Managing Director (Abstract Productions)
\professionalExperienceItem{October 2008}{October 2011}
{Managing Director}{Abstract Productions}
{Alongside with a close friend and business partner, I owned and operated my own
business providing audio and lighting equipment and technical services for live
music events, community events, wedding, parties and corporate events.

This was a great experience which greatly enhanced my leadership, teamwork and 
analytical skills. It also provided me with a great opportunity to improve my 
skills with HTML, PHP, CSS, Apache, Unix and MySQL as I was responsible for 
developing and maintaining the business' website. I decided to end my commitment
to the business as it was the not the field in which I intended to pursue a 
career.}
{
    % Programming languages
    \professionalTool{PHP}

    % Web development
    \professionalTool{HTML}
    \professionalTool{CSS}
    \professionalTool{jQuery}

    % Web administration
    \professionalTool{Apache}
    
    % Operating systems
    \professionalTool{Unix}
    
    % Databases
    \professionalTool{MySQL}
}

\end{professionalExperience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%
% \educationItem{beginYear}{endYear}{name}{institution}{\educationGrade{subject}{grade} ...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Education}
\begin{education}

\educationItem{2008}{2012}
{Bachelor of Engineering (Computer)}
{University of Sydney}
{}

\educationItem{2008}{2012}
{Bachelor of Science (Computer Science)}
{University of Sydney}
{}

\educationItem{2002}{2007}
{Higher School Certificate}
{Cherrybrook Technology High School}
{
    \educationGrade{Chemistry}{90/100}
    \educationGrade{English (Advanced)}{88/100}
    \educationGrade{Mathematics Extension 1}{97/100}
    \educationGrade{Mathematics Extension 2}{94/100}
    \educationGrade{Physics}{95/100}
    \educationGrade{UAI}{99.25}
}
\end{education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Licenses
%
% \licenseItem{name}{provider}{description}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Licenses}
\begin{licenses}
\licenseItem{Driver License}{RTA}{Class C Driver's License}
\licenseItem{Explosives License}{Workcover NSW}{Pyrotechnician's License (Organised 
Public Display, Ground display fireworks, Theatrical/indoor fireworks, Aerial 
shells up to 150 mm)}
\licenseItem{Boat Driver's License}{NSW Maritime}{Boat Driver's License}
\end{licenses}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Qualifications and Training
%
% \qualificationItem{date}{name}{description}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Qualifications and Training}
\begin{qualifications}

\qualificationItem{23 March 2011}
{Leadership Training}
{Participated in an internal leadership training program facilitated by 
\company{The Hills Shire Council}.}

\qualificationItem{28 February 2011}
{Senior First Aid}
{Statement of Attainment for fulfilling the requirements of 
\qualificationName{HLTFA301B (Apply First Aid)} from the 
\qualificationName{Health Training Package HLT07}.}

\qualificationItem{April 2010}
{Safety Checking Electrical Appliances}
{TAFE Statement in \qualificationName{Safety Checking Electrical Appliances}.}

\qualificationItem{2 December 2008}
{Responsible Service of Alcohol}
{Statement of Attainment for fulfilling the requirements of 
\qualificationName{THHBFB09B (Provide Responsible Service of Alcohol)} in 
partial completion of the \qualificationName{Certificate II in Hospitality 
(Operations)} qualification.}

\qualificationItem{26 February 2008}
{Turning Shoppers into Buyers}
{Certificate of achievement for participation in the \company{Jaycar} 
\qualificationName{Turning Shoppers into Buyers} Retail Sales Skills training.}

\qualificationItem{5 July 2007}
{Defensive Driving}
{Statement of Completion for completion of the \qualificationName{Murcotts Level
1 Defensive Driving Program} based on the unit of competence 
\qualificationName{TDTC197B (Drive Vehicle)} from the 
\qualificationName{Transport \& Distribution Package TDT02}.}

\end{qualifications}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Achievements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Awards and Achievements}
\begin{achievements}

\achievement{2008--2010}{Australian Power Institute Bursary}
{Awarded the \company{Australian Power Institute} Power Engineering Bursary. 
Rejected the bursary for the period 2011 onwards as I decided that this was not 
a field in which I wanted to pursue a career.}

\achievement{2008--2009}{University of Sydney: Talented Students Program}
{Admitted to the University of Sydney Talented Student Program, a program 
designed to make special arrangements which offer an intellectual challenge to 
elite students while they are studying at the University of Sydney.}

\achievement{2008}{University of Sydney: Advanced Engineering}
{Admitted to the \educationInstitute{University of Sydney} Advanced Engineering 
Program, designed to enable high achieving students to work on engineering and 
IT interdisciplinary project during their first semester.

My group was awarded the ``Best Project'' and ``Best Presentation'' for our 
Stirling engine project.}

\achievement{2007}{National Youth Science Forum}
{Was one of six Australian students to be selected to attend the ``Genesis 
Science \& Technology Summer School'' in Auckland, New Zealand.}

\end{achievements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References and Referees
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{References and Referees}
References and referees available on request.

\end{document}
