\begin{professionalExperience}

% Data Scientist (Freelancer.com)
\professionalExperienceItem{July 2012}{present}
{Data Scientist}{Freelancer.com}
{My job involved assisting in the design and implementation of software for use
by \company{Freelancer.com}. This included working with other staff to establish
technical specifications, developing the software and performing data analysis
techniques to improve key business metrics.}


% Tutor (University of Sydney)
\professionalExperienceItem{August 2012}{November 2012}
{Tutor}{University of Sydney}
{I was a tutor for a first year electrical engineering unit of study, named
``Foundations of Computer Systems'' (ELEC1601). This position involved preparing
and running three-hour laboratory session with up to 40 students in each
session.}
{}

% Tutor (University of Sydney)
\professionalExperienceItem{March 2012}{June 2012}
{Tutor}{University of Sydney}
{I was a tutor for a first year electrical engineering unit of study, named
``Fundamentals of Electrical and Electronic Engineering'' (ELEC1103). This
position involved preparing and running two-hour tutoring session with up to 40
students in each session.}

% Software Engineering Intern (Broadcom)
\professionalExperienceItem{November 2011}{February 2012}
{Software Engineering Intern}{Broadcom}
{This position was a great experience and allowed me to further my experience in
embedded computing. I was involved in developing the SDK for Broadcom's WICED
module (Wireless Internet Connectivity for Embedded Devices).

I completed two primary tasks during my employment. The major task was porting
``iperf'' (a network throughput management software) to the WICED development
system. In addition, I added the capability to trace thread execution of a Real
Time Operating System.}

% System Administrator (Audinate)
\professionalExperienceItem{April 2011}{July 2012}
{System Administrator}{Audinate}
{In this role I administered various servers running on either Ubuntu Server or
Sun Solaris. I administered various services including LDAP, ZFS (Zettabyte File
System), IMAP/SMTP (Zimbra) and NFS. I also worked extensively with VMware
Server during this role.

Through this position, I gained a wide range of experience including website
administration, Unix administration and designing and building dedicated Unix
servers.}

% Chief Pyrotechnician (Howard & Sons Pyrotechnics)
\professionalExperienceItem{July 2008}{present}
{Chief Pyrotechnician}{Howard \& Sons Pyrotechnics}
{I am a licensed pyrotechnician for a world-class pyrotechnics company. As a
chief pyrotechnician, I am responsible for many aspects of a pyrotechnics
display, including:
\begin{itemize}
    \item Managing the worksite and firing site.
    \item Managing the loading and unloading of fireworks.
    \item Dealing directly with clients and suppliers on-site.
    \item Responsibility for all rostered crew on-site.
    \item Responsibility for all Workplace Health \& Safety matters on-site.
\end{itemize}

In addition to my role as a pyrotechnician, I am also a pyrotechnic display
designer and am responsible for the planning, designing and choreography of a
pyrotechnics display to musical soundtracks.}

\end{professionalExperience}
