\begin{professionalExperience}

% Tutor (University of Sydney)
\professionalExperienceItem{August 2012}{present}
{Tutor}{University of Sydney}
{I was a tutor for a first year electrical engineering unit of study, named
``Foundations of Computer Systems'' (ELEC1601). This position involved preparing
and running three-hour laboratory session with up to 40 students in each
session.}
{}

% Engineering/Data Analytics Intern (Freelancer.com)
\professionalExperienceItem{July 2012}{present}
{Engineering/Data Analytics Intern}{Freelancer.com}
{My job involved assisting in the design and implementation of software for use
by \company{Freelancer.com}. This included working with other staff to establish
technical specifications, developing the software and performing data analysis
techniques to improve key business metrics.}
{
    % Programming languages
    \professionalTool{PHP}

    % Web development
    \professionalTool{CSS}
    \professionalTool{JavaScript}
    \professionalTool{HTML}
    \professionalTool{AJAX}
    \professionalTool{jQuery}
    \professionalTool{Twitter Bootstrap}

    % Web administration
    \professionalTool{NGINX}

    % Tools and editors
    \professionalTool{Git}
}

% Tutor (University of Sydney)
\professionalExperienceItem{March 2012}{June 2012}
{Tutor}{University of Sydney}
{I was a tutor for a first year electrical engineering unit of study, named
``Fundamentals of Electrical and Electronic Engineering'' (ELEC1103). This
position involved preparing and running two-hour tutoring session with up to 40
students in each session.}
{}

% Software Engineering Intern (Broadcom)
\professionalExperienceItem{November 2011}{February 2012}
{Software Engineering Intern}{Broadcom}
{This position was a great experience and allowed me to further my experience in
embedded computing. I was involved in developing the SDK for Broadcom's WICED
module (Wireless Internet Connectivity for Embedded Devices).

I completed two primary tasks during my employment. The major task was porting
``iperf'' (a network throughput management software) to the WICED development
system. In addition, I added the capability to trace thread execution of a Real
Time Operating System.}
{
    % Programming languages
    \professionalTool{C}
    \professionalTool{C++}
    \professionalTool{Perl}

    % Embedded programming
    \professionalTool{ThreadX}
    \professionalTool{NetX}
    \professionalTool{FreeRTOS}
    \professionalTool{LwIP}

    % Debugging
    \professionalTool{GDB}

    % Tools and editors
    \professionalTool{Eclipse IDE}
    \professionalTool{Subversion}
}

% System Administrator (Audinate)
\professionalExperienceItem{April 2011}{July 2012}
{System Administrator}{Audinate}
{In this role I administered various servers running on either Ubuntu Server or
Sun Solaris. I administered various services including LDAP, ZFS (Zettabyte File
System), IMAP/SMTP (Zimbra) and NFS. I also worked extensively with VMware
Server during this role.

Through this position, I gained a wide range of experience including website
administration, Unix administration and designing and building dedicated Unix
servers.}
{
    % Programming languages
    \professionalTool{PHP}

    % Shells
    \professionalTool{bash}

    % Web development
    \professionalTool{HTML}
    \professionalTool{CSS}
    \professionalTool{Joomla}

    % Web administration
    \professionalTool{Apache}

    % Database
    \professionalTool{MySQL}

    % Operating systems
    \professionalTool{Ubuntu Server}
    \professionalTool{Sun Solaris}

    % Other
    \professionalTool{Zettabyte File System (ZFS)}
    \professionalTool{Zimbra}
}

% Industrial Student (TransGrid)
\professionalExperienceItem{December 2010}{February 2011}
{Industrial Student}{TransGrid}
{In this position, I worked in the ``Projects (Central Region)'' section. I was
involved with various projects including earth grid safety inspections and
progress meetings with contractors.

This work experience was a paid work experience offered as a part of my
\company{Australian Power Institute} bursary.

Whilst at \company{TransGrid}, I developed a database utility using
Microsoft Access and Visual Basic to assist the projects team with managing and
tracking project completion. Whilst VBA is not a sophisticated or complicated
programming language, this was an interesting experience in which I was required
to write some sophisticated temporal SQL queries.}
{
    % Programming languages
    \professionalTool{Visual Basic for Applications (VBA)}
    \professionalTool{SQL}

    % Databases
    \professionalTool{Microsoft Access}
}

% Industrial Student (Australian Energy Market Operator)
\professionalExperienceItem{December 2009}{February 2010}
{Industrial Student}{Australian Energy Market Operator}
{I was working in the ``Metering \& Settlements'' team. This team had to deal
with large amounts of data existing in SQL tables which are updated hourly based
on real-time monitoring data.

This work experience was a paid work experience offered as a part of my
\company{Australian Power Institute} bursary.

My main role within the team was working on improving the reliability and
accuracy of the operations of the team by designing software-based tools to
allow them to monitor and analyse data. I analysed and reconstructed several
macro-enabled spreadsheets used by the team to perform important calculations. I
was able to improve the accuracy of the data reported by the spreadsheet and
greatly improve the running speeds of the tools.}
{
    % Programming languages
    \professionalTool{Visual Basic for Applications (VBA)}
    \professionalTool{SQL}

    % Databases
    \professionalTool{Oracle}
}

% Industrial Student (Energy Australia)
\professionalExperienceItem{February 2009}{February 2009}
{Industrial Student}{Energy Australia}
{In this role, I was involved with the ``Intelligent Networks'' division,
working on an electrical sensing and monitoring system. I was involved with
analysing system diagrams and attending regular meetings with engineers to
discuss implementation details for a smart metering device that was being
developed.

This work experience was a paid work experience offered as a part of my
\company{Australian Power Institute} bursary.}
{}

% Customer Service Officer (The Hills Shire Council)
\professionalExperienceItem{January 2009}{present}
{Customer Service Officer}{The Hills Shire Council}
{This role involved taking phone calls and handling enquiries regarding the
council's community halls and other related facilities, as well as entering
these details into a booking system and handling related activities such as
invoicing.

My role also involved completing room set ups and pack downs, as well as
supervising events taking place in the council facilities.}
{}

% Chief Pyrotechnician (Howard & Sons Pyrotechnics)
\professionalExperienceItem{July 2008}{present}
{Chief Pyrotechnician}{Howard \& Sons Pyrotechnics}
{I am a licensed pyrotechnician for a world-class pyrotechnics company. As a
chief pyrotechnician, I am responsible for many aspects of a pyrotechnics
display, including:
\begin{itemize}
    \item Managing the worksite and firing site.
    \item Managing the loading and unloading of fireworks.
    \item Dealing directly with clients and suppliers on-site.
    \item Responsibility for all rostered crew on-site.
    \item Responsibility for all Workplace Health \& Safety matters on-site.
\end{itemize}

In addition to my role as a pyrotechnician, I am also a pyrotechnic display
designer and am responsible for the planning, designing and choreography of a
pyrotechnics display to musical soundtracks.}
{}

\end{professionalExperience}
