\begin{qualifications}

\qualificationItem{23 March 2011}
{Leadership Training}
{Participated in an internal leadership training program facilitated by
\company{The Hills Shire Council}.}

\qualificationItem{28 February 2011}
{Senior First Aid}
{Statement of Attainment for fulfilling the requirements of
\qualificationName{HLTFA301B (Apply First Aid)} from the
\qualificationName{Health Training Package HLT07}.}

\qualificationItem{April 2010}
{Safety Checking Electrical Appliances}
{TAFE Statement in \qualificationName{Safety Checking Electrical Appliances}.}

\qualificationItem{2 December 2008}
{Responsible Service of Alcohol}
{Statement of Attainment for fulfilling the requirements of
\qualificationName{THHBFB09B (Provide Responsible Service of Alcohol)} in
partial completion of the \qualificationName{Certificate II in Hospitality
(Operations)} qualification.}

\qualificationItem{26 February 2008}
{Turning Shoppers into Buyers}
{Certificate of achievement for participation in the \company{Jaycar}
\qualificationName{Turning Shoppers into Buyers} Retail Sales Skills training.}

\qualificationItem{5 July 2007}
{Defensive Driving}
{Statement of Completion for completion of the \qualificationName{Murcotts Level
1 Defensive Driving Program} based on the unit of competence
\qualificationName{TDTC197B (Drive Vehicle)} from the
\qualificationName{Transport \& Distribution Package TDT02}.}

\end{qualifications}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Achievements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Awards and Achievements}
\begin{achievements}

\achievement{2008--2010}{Australian Power Institute Bursary}
{Awarded the \company{Australian Power Institute} Power Engineering Bursary.
Rejected the bursary for the period 2011 onwards as I decided that this was not
a field in which I wanted to pursue a career.}

\achievement{2008--2009}{University of Sydney: Talented Students Program}
{Admitted to the University of Sydney Talented Student Program, a program
designed to make special arrangements which offer an intellectual challenge to
elite students while they are studying at the University of Sydney.}

\achievement{2008}{University of Sydney: Advanced Engineering}
{Admitted to the \educationInstitute{University of Sydney} Advanced Engineering
Program, designed to enable high achieving students to work on engineering and
IT interdisciplinary project during their first semester.

My group was awarded the ``Best Project'' and ``Best Presentation'' for our
Stirling engine project.}

\achievement{2007}{National Youth Science Forum}
{Was one of six Australian students to be selected to attend the ``Genesis
Science \& Technology Summer School'' in Auckland, New Zealand.}

\end{achievements}
